A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-24 analysis/paper.Rmd

>>>>

For the calculation of bias, we used the formula provided in the original paper. 
$$ Relative bias = {\frac{IE_{survivors} - IE_{survivors&HIV deaths}}{IE_{survivors&HIV deaths}} $$        
$$ Absolute bias = IE_{survivors} - IE_{survivors&HIV deaths}$$    
According to [@quattrochi2019], ${IE_{survivors}$ was the estimates of U5M based on living women in 2010, and IE_{survivors&HIV deaths} was the estimates of U5M based on living women in 2010 and women died from HIV/AIDS before 2010 given the condition that they would have been 15-49 in 2010 if they had survived.
